MVT Normal: wide

### 2020-08-27 src/s_trends.Rmd
cleaned up graph and addressed Aki's comments

```{r}
res <- readRDS("../output/experiment_trends_all_dim.rds")
g <- 
  res %>%
  select(iters, trend, Rstar, Rstar_split) %>% 
  melt(id.vars=c("iters", "trend")) %>% 
  mutate(variable=case_when(variable=="Rstar"~"A. R*",
                            variable=="Rstar_split"~"B. split-R*")) %>% 
  ggplot(aes(y = value, x = trend)) + 
  geom_point() + 
  geom_jitter() + 
  facet_grid(vars(iters), vars(variable)) + 
  geom_hline(yintercept = 1) +
  theme(strip.text.x = element_text(size=12, colour="black"),
        strip.text.y = element_text(size=12, colour="black"),
        axis.text.x = element_text(size=10, colour="black"),
        axis.text.y = element_text(size=10, colour="black")) +
  xlab("Trend") +
  ylab("Value")
ggsave("../output/trends_all_dim.pdf", g, width = 8, height = 6)
```

@@

```{r}
g <- readRDS("../output/experiment_trends_joint_distribution.rds") %>%
  as.data.frame() %>% 
  select(iters, rho, rep, zsRhat, Rstar_split) %>% 
  unique() %>%
  select(-rep) %>% 
  melt(c("rho", "iters"))  %>% 
  mutate(variable=case_when(variable=="zsRhat"~"A. split-Rhat",
                            variable=="Rstar_split"~"B. split-R*")) %>% 
  ggplot(aes(y = value, x = rho)) + 
  geom_jitter() + 
  facet_grid(vars(iters), vars(variable)) + 
  geom_hline(yintercept = 1) +
  theme(strip.text.x = element_text(size=12, colour="black"),
        strip.text.y = element_text(size=12, colour="black"),
        axis.text.x = element_text(size=10, colour="black"),
        axis.text.y = element_text(size=10, colour="black")) +
  ylab("Value") +
  xlab(TeX("$\\rho$"))
g

@@

ggplot(data = res, aes(x = rho, y = Rstar_split)) + 
  geom_jitter() + 
  facet_grid(vars(iters)) + 
  geom_hline(yintercept = 1) + 
  ggtitle('Split-R*') +
  ylim(0, 6)
```

>>>>

```{r}
res <- readRDS("../output/experiment_trends_all_dim.rds")
g <- 
  res %>%
  select(iters, trend, Rstar, Rstar_split) %>% 
  melt(id.vars=c("iters", "trend")) %>% 
  mutate(variable=case_when(variable=="Rstar"~"A. R*",
                            variable=="Rstar_split"~"B. Split-R*")) %>% 
  ggplot(aes(y = value, x = trend)) + 
  geom_point() + 
  geom_jitter() + 
  facet_grid(vars(iters), vars(variable)) + 
  geom_hline(yintercept = 1) +
  theme(strip.text.x = element_text(size=12, colour="black"),
        strip.text.y = element_text(size=12, colour="black"),
        axis.text.x = element_text(size=10, colour="black"),
        axis.text.y = element_text(size=10, colour="black")) +
  xlab("Trend") +
  ylab("Value")
ggsave("../output/trends_all_dim.pdf", g, width = 8, height = 6)
```

@@

```{r}
g <- readRDS("../output/experiment_trends_joint_distribution.rds") %>%
  as.data.frame() %>% 
  select(iters, rho, rep, zsRhat, Rstar_split) %>% 
  unique() %>%
  select(-rep) %>% 
  melt(c("rho", "iters"))  %>% 
  mutate(variable=case_when(variable=="zsRhat"~"A. Split-Rhat",
                            variable=="Rstar_split"~"B. Split-R*")) %>% 
  ggplot(aes(y = value, x = rho)) + 
  geom_jitter() + 
  facet_grid(vars(iters), vars(variable)) + 
  geom_hline(yintercept = 1) +
  theme(strip.text.x = element_text(size=12, colour="black"),
        strip.text.y = element_text(size=12, colour="black"),
        axis.text.x = element_text(size=10, colour="black"),
        axis.text.y = element_text(size=10, colour="black")) +
  ylab("Value") +
  xlab(TeX("$\\rho$"))
g

@@

g <- ggplot(data = res, aes(x = rho, y = Rstar_split)) + 
  geom_jitter() + 
  facet_grid(vars(iters)) + 
  geom_hline(yintercept = 1) + 
  ylab(TeX("Split-R*")) +
  xlab(TeX("$\\rho$")) +
  ylim(0, 6) +
  theme(strip.text.x = element_text(size=12, colour="black"),
        strip.text.y = element_text(size=12, colour="black"),
        axis.text.x = element_text(size=10, colour="black"),
        axis.text.y = element_text(size=10, colour="black"))
ggsave("../output/trends_ar1.pdf", g, width = 8, height = 6)

b_sum <- res %>%
  group_by(iters, rho) %>% 
  summarise(lower=quantile(Rstar_split, 0.025),
            upper=quantile(Rstar_split, 0.975),
            Rstar_split=median(Rstar_split)) %>% 
  mutate(type="summary")
res1 <- res %>%
  bind_rows(b_sum)

g <- ggplot(data = filter(res1, is.na(type)), aes(x = as.factor(iters), y = Rstar_split, group=rho)) + 
  geom_jitter(width = 0.2, height = 0, colour="grey") + 
  geom_pointrange(data=filter(res1, !is.na(type)), aes(ymin=lower, ymax=upper)) +
  geom_line(data=filter(res1, !is.na(type))) +
  facet_wrap(~rho, scales="free") + 
  geom_hline(yintercept = 1) + 
  ylab(TeX("Split-R*")) +
  xlab("# iterations") +
  theme(strip.text.x = element_text(size=12, colour="black"),
        strip.text.y = element_text(size=12, colour="black"),
        axis.text.x = element_text(size=10, colour="black"),
        axis.text.y = element_text(size=10, colour="black"))

ggsave("../output/trends_ar1_transposed.pdf", g, width = 8, height = 6)
```

### 2020-08-27 src/s_wide_distributions.Rmd
cleaned up graph and addressed Aki's comments

a_df <- a_df %>%
  mutate(samples_ncp=r_star)
saveRDS(a_df, "../output/mvt_500_all.rds")
a_df <- readRDS("../output/mvt_500_all.rds")
g <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("Model", labels=c("centered", "non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8)) +
  ggtitle("A.")
# ggsave("../output/wide_data.pdf", g, width = 12, height = 8)

@@

a_df <- a_df %>%
  tibble(samples_1000=r_star1)
saveRDS(a_df, "../output/mvt_wide_summaries.rds")
mon <- monitor_extra(split_data(full_data))
mean(mon$zfsRhat>1.01)
mean(mon$zsseff<400)
mean(mon$tailseff<400)
a_df <- readRDS("../output/mvt_wide_summaries.rds")
a_df <- tibble(samples_400=a_df$.$samples_400, samples_1000=a_df$samples_1000)
g1 <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("# of draws", labels=c("400", "1000")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black"),
        legend.position = c(0.8, 0.8)) +
  ggtitle("B.")
ggsave("../output/very_wide_data.pdf", g, width = 12, height = 8)
```

>>>>

a_df <- a_df %>%
  mutate(samples_ncp=r_star)
saveRDS(a_df, "../output/mvt_500_all.rds")
a_df <- readRDS("../output/mvt_500_all.rds")
g <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("Model", labels=c("Centered", "Non-centered")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.8, 0.8)) +
  ggtitle("A.")
# ggsave("../output/wide_data.pdf", g, width = 12, height = 8)

@@

a_df <- a_df %>%
  tibble(samples_1000=r_star1)
saveRDS(a_df, "../output/mvt_wide_summaries.rds")
mon <- monitor_extra(split_data(full_data))
mean(mon$zfsRhat>1.01)
mean(mon$zsseff<400)
mean(mon$tailseff<400)
a_df <- readRDS("../output/mvt_wide_summaries.rds")
a_df <- tibble(samples_400=a_df$.$samples_400, samples_1000=a_df$samples_1000)
g1 <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position="identity", alpha=0.8, bins=20) +
  scale_fill_grey("# of draws", labels=c("400", "1000")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=14, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.8, 0.8)) +
  ggtitle("B.")
ggsave("../output/very_wide_data.pdf", g, width = 12, height = 8)
```
